%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        
        \resumeProjectHeading
          {\textbf{ML Model Performance Monitoring System} $|$ \emph{databricks, pyspark}}{\textbf{Jun 2025 -- Aug 2025}}
          \resumeItemListStart
    \resumeItem{Instrumented statistical drift detection metrics \textbf{(KS, Lift)} to monitor large-scale marketing campaign models.}
\resumeItem{Built a Databricks monitoring framework for \textbf{25 ML models} (LR, GBM, RF) with statistical threshold alerts.}
\resumeItem{Developed automated pyspark pipeline to process \textbf{3B+ scored records} for realtime performance, drift analysis.}
\resumeItem{Identified, flagged \textbf{degrading models} enabling timely retraining, increasing campaign conversion rate by \textbf{15\%}.}



  \resumeItemListEnd
    
    \resumeProjectHeading
          {\textbf{AskNEU RAG System} $|$ \emph{RAG, LangChain, Docker, Pinecone, GCP} \ {\href{https://github.com/justin-aj/AskNEU}{[link]}}}{\textbf{Jan 2025 -- Apr 2025}}
          \resumeItemListStart
            \resumeItem{Architected RAG system with Cohere reranking, direct and Complex Retrieval Framework of documents with query decomposition, context unification using GPT-4.1, Gemini 2.0 APIs and \textbf{LangGraph} for workflow.} 
            \resumeItem{Engineered automated data pipeline to scrape \textbf{50,000+ NEU sites Crawl4AI, Selenium}, chunking, ingest embeddings into \textbf{Pinecone vector DB} with LangChain wrappers to semantic search enabled knowledge base.}
            \resumeItem{Ensured scalability with \textbf{Docker} containers, orchestrating ETL data pipeline(\textbf{Airflow DAGs}), GitHub Actions for CI/CD, leveraging \textbf{Kubernetes} clusters with terraform for automated deployment, \textbf{Grafana} for monitoring.}
          \resumeItemListEnd

          
    % \resumeProjectHeading
    %       {\textbf{AI Banking Assistant} $|$ \emph{transformers, peft, huggingface, pytorch} \ {\href{https://github.com/justin-aj/AIBankingAssistant}{[link]}}}{\textbf{Dec 2024 -- Jan 2025}}
    %       \resumeItemListStart
    %         \resumeItem{Architected question answering and conditional generation tasks, processing \textbf{25000+} QA pairs.}
    %         \resumeItem{Fine-tuned \textbf{T5-small, GPT2-small, DistilBERT} using PEFT(QLoRA) with \textbf{4-bit quantization.}}
    %         \resumeItem{Achieved a \textbf{BLEU score of 0.25} and \textbf{ROUGE-1 F1 score of 0.54} indicating strong model performance in text generation tasks by fine-tuning and benchmarking a \textbf{Falcon-7B}-based model on \textbf{NVIDIA v100 GPU} \textbf{CUDA}.}

          % \resumeItemListEnd
    \resumeProjectHeading
          {\textbf{Food Categorization using Machine Learning} $|$ \emph{sklearn, Random Forest} {\href{https://github.com/justin-aj/USDA-Branded-Foods}{[link]}}}{\textbf{Oct 2024 -- Dec 2024}}
          \resumeItemListStart
            \resumeItem{Developed an automated machine learning system to categorize food products using data from the USDA.}
            \resumeItem{Applied Logistic Regression and Random Forest, achieving \textbf{91.98\% accuracy, 91.87\% F1-Score on 1.7M entries}. Enhanced performance through TF-IDF vectorization, PCA dimensionality reduction, A/B testing.}
            \resumeItem{Derived statistical insights for nutrition, inventory management, leveraging \textbf{hypothesis testing, ANOVA}.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%
\end{document}
